### 2017-12-31 README.Rmd
Add codecov

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)

The objective of this package is to perform inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.

>>>>

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
